A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-19 paper.tex
Added acknowledgements.
remove solution2 and 4

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & 43.3GB & 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of actually used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
program is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 43.3GB of that are the input Ntuples,
and of those only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
but only 448.3MB in source are checked out, and the software actually used only
measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
whether it is needed or not.

@@

Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
through several stages which make it more suitable for preservation.
In each step of evolution, we make the dependencies of the artifact
more explicit and available for analysis and automated processing.
As noted in the previous section, the original author provided us with
prose instructions by email which we translated into an
executable script.  The executable script has embedded in it
a number of external identifiers such as URLs pointing to repositories
and paths to networked filesystems.  As a general programming practice,
embedding such constants into the middle of a program is unwise, and so
we extract all of those identifiers and place them \emph{outside} the
script in a \emph{dependency map} or just \emph{map} for short.
The dependency map lists all of the external dependencies of the application, indicating
the type, how they are accessed, and where they are currently located.
The resulting script then simply refers to abstract file locations such
as \verb$GIT$ and \verb!$CMSSW!, while the map file indicates where they
are currently located. If properly constructed, the script should not refer to any external
resource unless it is indicated in the dependency map.  We call this idealized
artifact an \emph{abstract script}.

By extracting the dependencies into the dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
If we group the script, dependency map, and dependencies into a \emph{package},
we now have a self-contained artifact that can be moved from place to place.
In some cases, it may be safe to allow the dependency map to refer to 
trusted remote repositories.  Whether this is advisable is a judgement that
must be made by the user or the curator, taking into account the long-term
stability of said repositories.

@@

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
he modification of the package only introduces the minimal changes of the map file on the client side.

@@

Parrot is a virtual filesystem access tool which has previously been used to attach
exisiting programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files:    & 1632         & 15642\\ 
\hline
    Empty Files:    & 14273        & 263\\
\hline
    Directories:    & 1549         & 1549\\ 
\hline
    Symbolic Links: & 4614         & ??? \\
\hline
    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the application was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

We first repeated the example from scratch using Solution 2 on the original machine and counted the time consumption and data size. 
Then based on the successful execution of Solution 2, Solution 4 is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively. Solution 4 also counted the time used to obtain the filename list and generate the package. To measure data size, we can easily figure out the size of each data and code source easily inside the package under Solution 4.
Solution 2 does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Solution 2 and 4.
Solution 4 is faster than Solution 2, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 4 seconds.
We were surprised that Solution 4 even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Solution 2, but is copied into the package in Solution 4. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

@@

Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
The third column corresponds to the data size of Solution 4 and can be easily figured out, because all the necessary data has been copied into the package.
Solution 2 does not support measuring implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

To further verify the correctness of Solution 4 on other machines, two different machines are employed -
one virtual
machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.

@@

\section{Conclusion}

@@

>>>>

\begin{table}[t]
    \centering
    \small
    \begin{tabular}{|l|l|r|r|r|}
        \hline
        \bf Name & \bf Location & \bf Total & \bf Named & \bf Used \\ 
        \hline
        CMSSW code     & CVS & 88.1GB & 448.3MB & 6.3MB\\ \hline
        Tau source       & Git & 73.7MB & 73.7MB & 6.7MB \\ \hline
        PyYAML binaries    & HTTP & 52MB & 52MB & 0KB \\ \hline
        .h file       & HTTP& 41KB & 41KB & 0KB \\ \hline \hline
        Ntuples data    & HDFS& 11.6TB & N/A& 20GB \\ \hline
        Configuration & CVMFS & 7.4GB & N/A & 103MB \\ \hline
        Linux commands & localFS & 110GB &  N/A & 68.4MB \\ \hline     
        HOME dir& AFS &12GB & N/A & 32MB\\ \hline
        Misc commands & PanFS & 155TB & N/A  & 1.6MB \\ \hline
        Total      &    & 166.8TB            & N/A & 21GB \\ \hline
    \end{tabular}
    \begin{tablenotes}
      \small
      \item The first column illustrates the total size of each data and software source; 
            the second column illustrates the size of the named files from each source;
            the third column illustrates the size of actually used data from each source.
            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
    \end{tablenotes}
    \caption{Data and Code Used by Tau Roast}
    \label{table:size-original-real}
\end{table}

@@

\item {\bf High Selectivity.}  Although the total size of the resources accessed by this
program is very large, the size of the data and software actually used are much smaller.
Often, an entire repository or data source is named within the script, but the program
only needs a handful of items from that source.  For example, the data is stored on an
HDFS filesystem with 11.6TB of data, but only 20GB are actually consumed by the program. The CMSSW repository is 88.1GB in total
but only 448.3MB in source are checked out, and the software actually used only
measured 6.3MB.  In a few cases, a source of software is named but never actually accessed.
(For example, our original script includes the Open Science Grid software stack in the PATH, but does not actually use it.)
We suspect that end users are accustomed to missing dependencies and thus get in the habit of adding commonly used software,
whether it is needed or not.

@@

Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
through several stages which make it more suitable for preservation.
In each step of evolution, we make the dependencies of the artifact
more explicit and available for analysis and automated processing.
As noted in the previous section, the original author provided us with
prose instructions by email which we translated into an
executable script.  The executable script has embedded in it
a number of external identifiers such as URLs pointing to repositories
and paths to networked filesystems.  As a general programming practice,
embedding such constants into the middle of a program is unwise, and so
we extract all of those identifiers and place them \emph{outside} the
script in a \emph{dependency map} or just \emph{map} for short.
The dependency map lists all of the external dependencies of the application, indicating
the type, how they are accessed, and where they are currently located.
The resulting script then simply refers to abstract file locations such
as \verb$GIT$ and \verb$CVMFS$, while the map file indicates where they
are currently located. If properly constructed, the script should not refer to any external
resource unless it is indicated in the dependency map.  We call this idealized
artifact an \emph{abstract script}.

By extracting the dependencies into the dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
If we group the script, dependency map, and dependencies into a \emph{package},
we now have a self-contained artifact that can be moved from place to place.
In some cases, it may be safe to allow the dependency map to refer to 
trusted remote repositories.  Whether this is advisable is a judgment that
must be made by the user or the curator, taking into account the long-term
stability of said repositories.

However, only having the package and the dependency map is not enough. The successful execution of the application on the original machine also relies on the configuration of environment variables.
We collected the environment variables of the original machine and transformed it into one executable script. If another researcher wants to repeat the application, this executable script will be first executed.

@@

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{/data/git/cms-ttH} and the real location of dependency variable {\tt CVMFS}
is {\tt /data/cvmfs/grid.cern.ch}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

@@

Parrot is a virtual filesystem access tool which has previously been used to attach
existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

@@

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files:    & 1632         & 15642\\ 
\hline
    Empty Files:    & 14273        & 263\\
\hline
    Directories:    & 1549         & 1549\\ 
\hline
    Symbolic Links: & 4614         & 4614 \\
\hline
    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

We evaluated the correctness of the reduced package and the overhead of generating the package.
To do it, the application was repeated with the help of Script (as shown in Figure~\ref{fig:version-evolution}) on the original machine, mentioned as {\bf Script-Solution} in the following part, 
one reduced package was generated and verified with the help of Parrot on the original machine, which will be mentioned as {\bf Package-Solution}.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of the reduced package.

We first repeated the example from scratch using the Script translated from the original email on the original machine and counted the time consumption and data size. 
Then based on the successful execution of Script-Solution, Package-Solution is evaluated - one package containing necessary dependencies is generated, and then the time consumption and data size is analyzed.

To measure time consumption, we counted the time used to obtain remote software dependencies, build environment, and analyze the dataset respectively. We also counted the time used to obtain the filename list and generate the package. To measure data size, we can easily figure out the size of each data and code source inside the package under Package-Solution.
Script-Solution does not support mining of implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

Table~\ref{table:time-2nd3rd} shows the execution time comparison between
Script-Solution and Package-Solution.
Package-Solution is faster than Script-Solution, because all the software copied into the package has been compiled and the Software Acquisition stage is not necessary.
and all the environment building only takes 4 seconds.
We were surprised that Package-Solution even reduces the actual analysis time. 
The reason for this is that data is obtained through accessing HDFS in Script-Solution, but is copied into the package in Package-Solution. This localization of experimental data speeds up the data analysis process, resulting the actual analysis time reducing from 20 minutes to 13 minutes.

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Script-Solution and Package-Solution}
    \label{table:time-2nd3rd}
\end{table}

@@

Table~\ref{table:size-original-real} illustrates the total size, named size in the example and actually used size of each remote source (the first 4 items) and local source (the remaining 5 items).
The third column corresponds to the data size of Package-Solution and can be easily figured out, because all the necessary data has been copied into the package.
Script-Solution does not support measuring implicit dependencies. As for remote sources, we can figure out the named size through the analysis script. However, it is hard to figure out the named size of each local source. 
Instead, we only knew that total size of each file system is very large.

To further verify the correctness of Package-Solution on other machines, two different machines are employed -
one virtual
machine~\cite{goldberg1974survey} from Notre Dame Cloud Platform based on KVM sharing the same kernel version with the original machine,
and one virtual machine from amazon EC2~\cite{amazon2010amazon} based on Xen.

@@

\section{Postscript}

@@

\section{*Acknowledgments}

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS)
and OCI-1148330 (SI2).  We also thank...
